Corilation Compare!

### 2022-11-15 graphs_newt_snakes/corcompare.Rmd
Looked at more data and added maps to my slim script! Need to fix corcompare to look nicer and spend a lot of time writing about all of these new results.
I finished the write up for cor compare

---
title: "Cor Compare"
output: html_document
date: '2022-08-26'
---

@@

## Corilation Compare!

I have run four separate experiments and now I will compare their different correlations to see if I can tell the difference between each of the four experiments.

@@

I am investigating the correlation calculations. I predicted that though co-evolution (interaction & evolution) species' phenotypes would become spatially correlated. I saw some very high correlations (around 0.5) in some of these simulations. To see if there is a difference between the correlations in my experiment I will create some comparative histograms.

@@

-  5 sections & 7 sections will have *similar* correlation distributions
- no heritability & no interaction correlation distributions will look *very different* from 5 sections & 7 sections

@@

@@

all_cor_exp %>%
  group_by(experiment) %>%
  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)

@@

exclude_b <- all_the_means[which(all_the_means$exp!='B'),]
exclude_c <- all_the_means[which(all_the_means$exp!='C'),]

print("Anovas from mean of A and B")
res.aov2ab <- aov(name ~ exp, data = exclude_c[which(exclude_c$exp!='D'),])
summary(res.aov2ab)
print("Anovas from mean of A and C")
res.aov2ac <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='D'),])
summary(res.aov2ac)
print("Anovas from mean of A and D")
res.aov2ad <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='C'),])
summary(res.aov2ad)
print("Anovas from mean of C and D")
res.aov2cd <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='A'),])
summary(res.aov2cd)
```

I want to compare the different cor values from the simulations, but i also want to look at it simulation by simulation.

I think trials within a simulation experiment (A, B, C, D) should be the same (same mu and mu effect size).

They should also be different between different GA combinations

same GA should be different in the different experiments

@@

wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB

wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC

wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD

wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC

wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD

wilcox.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD

@@

#t.test(GA1_cor_tall_file[GA1_cor_tall_file$group == "1e-08_0.005_1e-08_0.005" & GA1_cor_tall_file$rep <= 1,]$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_file[GA1_cor_tall_file$group == "1e-08_0.005_1e-08_0.005" & GA1_cor_tall_file$rep >= 2,]$mean_newt_pheno_By_mean_snake_pheno) #AA

t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC

t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD

t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC

t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD

t.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD

t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB

@@

```{r, distribuuution plots, fig.height = 11, fig.width = 5}

@@

ggplot(all_cor_exp[which(all_cor_exp$gen>=min_gen & all_cor_exp$gen<=max_gen),])+
   #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  #xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=mean_newt_pheno_By_mean_snake_pheno, fill=experiment))+ #, y=threshold
 # theme(plot.title = element_text(size=5)) +
 # xlim(-.1, 1.1)+
  #geom_vline(data = dummy, aes(xintercept = name))+
  facet_grid(group~experiment)+
  #facet_wrap(~group_exp)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
                    strip.background = element_blank(), strip.text.x = element_blank(),
                   title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                    axis.title.y = element_blank())
```

@@

```{r, cor com figs}

@@

ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

@@

```{r, density com figs}

ginmin = 0
ginmax = 5000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 5000
ginmax = 10000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 10000
ginmax = 15000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 15000
ginmax = 20000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 20000
ginmax = 25000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 25000
ginmax = 30000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 30000
ginmax = 35000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 35000
ginmax = 40000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 40000
ginmax = 45000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

ginmin = 45000
ginmax = 50000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

@@

```{r, one big one}

ginmin = 0
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

@@

# next step is to count the high and the lows 
like make a lower limit like must be above 0.3

```{r, thresholds}

@@

@@

file = all_cor_exp
treshold = 0.5
p_n_b = "b"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

file = all_cor_exp
treshold = 0.7
p_n_b = "b"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

file = all_cor_exp
treshold = 0.7
p_n_b = "b"
min_gen = 100
max_gen =50000
whichgroup = "experiment"
```

```{r, ggslide test}

ggplot(all_cor_exp) + 
  #geom_point(size = 2) +
  #geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, group=rep))+
  geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity")+
  #geom_xsidehistogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity") +
  geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
  scale_ysidex_discrete(guide = guide_axis(angle = 45))

@@

>>>>

---
title: "Corilation Compare!"
output: html_document
date: '2022-08-26'
---

@@

## Background

I have run four separate experiments and now I will compare their different phenotype spatial correlations to see if I can tell the difference between each of the four experiments.

@@

I am investigating the spatial phenotype correlation calculations. I predicted that though co-evolution (interaction & evolution) species' phenotypes would become spatially correlated. I saw some very high correlations (around 0.5) in some of these simulations. To see if there is a difference between the correlations in my experiment I will create some comparative histograms.

@@

-  5 sections & 7 sections will have **similar** correlation distributions
- no heritability & no interaction correlation distributions will look **very different** from 5 sections & 7 sections

@@

First, I will try comparing the mean spatial correlations between the different experiments. Now within these four experiments, there are 16 GA combinations, which can have an effect on spatial phenotype correlation. Because each of these experiments contain the same GA combinations and the same amount of trials, it should be okay to compare them.

Note: Some of the simulations had fewer data points (data collected every 20 generations instead of 10). To account for fewer data points in some of the simulations, I cut about half of the data (everything had matching generations).

Here are the mean spatial phenotype correlation values:

@@

all_cor_exp %>%
  group_by(experiment) %>%
  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)
```

I ran some anovas to compare the spatial correlations between the different experiments. First, I got one mean per GA combination. So all four trials were combined to create one spatial correlation mean.

```{r, mean anovas}
#print("One mean per GA")

@@

exclude_a <- all_the_means[which(all_the_means$exp!='A'),]
exclude_b <- all_the_means[which(all_the_means$exp!='B'),]
exclude_c <- all_the_means[which(all_the_means$exp!='C'),]

#print("Anovas from mean of A and B")
res.aov2ab <- aov(name ~ exp, data = exclude_c[which(exclude_c$exp!='D'),])
MYaov2ab = unlist(summary(res.aov2ab))
print(paste0("Anovas from mean of A and B, F value: ", MYaov2ab[7], " Pr(>F) value: ",MYaov2ab[9]))

#print("Anovas from mean of A and C")
res.aov2ac <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='D'),])
MYaov2ac <- unlist(summary(res.aov2ac))
print(paste0("Anovas from mean of A and C, F value: ", MYaov2ac[7], " Pr(>F) value: ",MYaov2ac[9]))

#print("Anovas from mean of B and C")
res.aov2bc <- aov(name ~ exp, data = exclude_a[which(exclude_a$exp!='D'),])
MYaov2bc <- unlist(summary(res.aov2bc))
print(paste0("Anovas from mean of B and C, F value: ", MYaov2bc[7], " Pr(>F) value: ",MYaov2bc[9]))

#print("Anovas from mean of A and D")
res.aov2ad <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='C'),])
MYaov2ad <- unlist(summary(res.aov2ad))
print(paste0("Anovas from mean of A and D, F value: ", MYaov2ad[7], " Pr(>F) value: ",MYaov2ad[9]))

#print("Anovas from mean of B and D")
res.aov2bd <- aov(name ~ exp, data = exclude_a[which(exclude_a$exp!='C'),])
MYaov2bd <- unlist(summary(res.aov2bd))
print(paste0("Anovas from mean of B and D, F value: ", MYaov2bd[7], " Pr(>F) value: ",MYaov2bd[9]))

#print("Anovas from mean of C and D")
res.aov2cd <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='A'),])
MYaov2cd <- unlist(summary(res.aov2cd))
print(paste0("Anovas from mean of C and D, F value: ", MYaov2cd[7], " Pr(>F) value: ",MYaov2cd[9]))
```

I ran some more anovas to compare the spatial correlations between the different experiments. This time there is one mean per GA combination trial. So all four trials have their own spatial correlation mean.

```{r, second anavo one mean per rep}
#print("One mean per rep")

all_the_means_byrep = all_cor_exp %>%
  group_by(group_exp_rep) %>%
  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)

all_the_means_byrep$exp <- str_split_fixed(all_the_means_byrep$group_exp_rep, "_", 6)[,5]

exclude_a <- all_the_means_byrep[which(all_the_means_byrep$exp!='A'),]
exclude_b <- all_the_means_byrep[which(all_the_means_byrep$exp!='B'),]
exclude_c <- all_the_means_byrep[which(all_the_means_byrep$exp!='C'),]

#print("Anovas from mean of A and B")
res.aov2ab <- aov(name ~ exp, data = exclude_c[which(exclude_c$exp!='D'),])
MYaov2ab <- unlist(summary(res.aov2ab))
print(paste0("Anovas from mean of A and B, F value: ", MYaov2ab[7], " Pr(>F) value: ",MYaov2ab[9]))

#print("Anovas from mean of A and C")
res.aov2ac <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='D'),])
MYaov2ac <- unlist(summary(res.aov2ac))
print(paste0("Anovas from mean of A and C, F value: ", MYaov2ac[7], " Pr(>F) value: ",MYaov2ac[9]))

#print("Anovas from mean of B and C")
res.aov2bc <- aov(name ~ exp, data = exclude_a[which(exclude_a$exp!='D'),])
MYaov2bc <- unlist(summary(res.aov2bc))
print(paste0("Anovas from mean of B and C, F value: ", MYaov2bc[7], " Pr(>F) value: ",MYaov2bc[9]))

#print("Anovas from mean of A and D")
res.aov2ad <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='C'),])
MYaov2ad <- unlist(summary(res.aov2ad))
print(paste0("Anovas from mean of A and D, F value: ", MYaov2ad[7], " Pr(>F) value: ",MYaov2ad[9]))

#print("Anovas from mean of B and D")
res.aov2bd <- aov(name ~ exp, data = exclude_a[which(exclude_a$exp!='C'),])
MYaov2bd <- unlist(summary(res.aov2bd))
print(paste0("Anovas from mean of B and D, F value: ", MYaov2bd[7], " Pr(>F) value: ",MYaov2bd[9]))

#print("Anovas from mean of C and D")
res.aov2cd <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='A'),])
MYaov2cd <- unlist(summary(res.aov2cd))
print(paste0("Anovas from mean of C and D, F value: ", MYaov2cd[7], " Pr(>F) value: ",MYaov2cd[9]))
```

Instead on taking the mean spatial correlation, I wanted to compare the series of correlation values from the each of my GA combinations. I think trials within a simulation experiment (A, B, C, D) should be the same (same mu and mu effect size). The spatial correlation might be different between different GA combinations within an experiment (A, B, C, D), but different between these experiments. Its a bit difficult to split my data up to make these comparisons, but I did run some wilcoxon tests and t-tests. Most everything was significantly different (only tested between experiments) in the wilcoxon test. In the Two Sample t-test when compering experiments AC, AD, BC, BD were different, but CD was not different. The Two Sample t-test between AB as only slightly different p-value = 0.02601.

@@

# wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB
# 
# wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC
# 
# wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD
# 
# wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC
# 
# wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD
# 
# wilcox.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD

@@

#t.test(GA1_cor_tall_file[GA1_cor_tall_file$group == "1e-08_0.005_1e-08_0.005" & GA1_cor_tall_file$rep <= 1,]$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_file[GA1_cor_tall_file$group == "1e-08_0.005_1e-08_0.005" & GA1_cor_tall_file$rep >= 2,]$mean_newt_pheno_By_mean_snake_pheno) #AA
# 
# t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC
# 
# t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD
# 
# t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC
# 
# t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD
# 
# t.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD
# 
# 
# t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB

@@

## Distribution Plot

In this section I examine the distribution of spatial phenotype correlation between each of the four experiments by genetic architecture (GA) combination. In this figure there are 4 trials per GA combination and experiment. There are sixteen GA combinations and four experiments (red = tall map 5 sections, green = tall map 7 sections, blue = no heritability, purple = no interaction). The labels on the right are the GA combinations.

```{r, distribuuution plots, fig.height = 11, fig.width = 8}

max_gen=5000
min_gen=100

@@

ggplot(all_cor_exp[which(all_cor_exp$gen>=min_gen & all_cor_exp$gen<=max_gen),])+
   #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  #xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=mean_newt_pheno_By_mean_snake_pheno, fill=experiment))+ #, y=threshold
 # theme(plot.title = element_text(size=5)) +
 # xlim(-.1, 1.1)+
  #geom_vline(data = dummy, aes(xintercept = name))+
  facet_grid(group~experiment)+
  #facet_wrap(~group_exp)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
                      strip.text.y = element_text(angle = 45, size = 6),
                    strip.background = element_blank(), strip.text.x = element_blank(),
                   title =element_text(size=4, face='bold'), axis.title.x = element_blank(),
                    axis.title.y = element_blank())
```

This plot is not the easiest to read. However, after staring at if for awhile I noticed that the no heritability experiment did not change between GA combos. Red (tall map 5 sections), green (tall map 7 sections), and purple (no interaction) look very similar for some of the GA combinations, but differ in GA combinations where the mutational variance in both the newts and snakes was high. I thought the distributions between A and B would be more similar. The mean of experiment B results seems to be similar to experiment A, but the distribution seems a bit more narrow. It is very difficult to tell if things are truly similar or different.

## Whole Distribution Plot

In this section I combine all of the trails and GA combinations to see if the spatial correlation distribution differs overall between the experiments. Here red is the tall map 5 sections, green is the tall map 7 sections, blue is the experiment that has no heritability, and purple there is no interaction.

@@

There are some very noticeable differences between the four experiments. One the mean of experiment A and B (tall map 5 sections & tall map 7 sections) are very similar, both are positive. Experiment B is narrower than experiment A. Experiment C is a perfect histogram with a mean at 0. Experiment D has a similar width to experiment A, but the mean is closer to 0.

## Spatial Correlation Over Time {.tabset}

In this sections I will walk through the spatial phenotype correlates of all 4 experiments in 5,000 generation chunks. The color represents the experiment (red = tall map 5 sections, green = tall map 7 sections, blue = no heritability, purple = no interaction). One type of plot is a general histogram an the other is a density plot. They are not stacked. The goal of these plots is to see how spatial correlation changes as time increases. The dashed line is the real newt and snake spatial phenotype correlation.

### Section 1
```{r, cor com figs 1}

@@

@@

### Section 2
```{r, cor com figs 2}

ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 3
```{r, cor com figs 3}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 4
```{r, cor com figs 4}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 5
```{r, cor com figs 5}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 6
```{r, cor com figs 6}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 7
```{r, cor com figs 7}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 8
```{r, cor com figs 8}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 9
```{r, cor com figs 9}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 10
```{r, cor com figs 10}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

@@

## {-}

## {.tabset}

### Section 1
```{r, density com figs 1}

ginmin = 0
ginmax = 5000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 2
```{r, density com figs 2}
ginmin = 5000
ginmax = 10000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 3
```{r, density com figs 3}
ginmin = 10000
ginmax = 15000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 4
```{r, density com figs 4}
ginmin = 15000
ginmax = 20000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 5
```{r, density com figs 5}
ginmin = 20000
ginmax = 25000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 6
```{r, density com figs 6}
ginmin = 25000
ginmax = 30000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 7
```{r, density com figs 7}
ginmin = 30000
ginmax = 35000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 8
```{r, density com figs 8}
ginmin = 35000
ginmax = 40000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 9
```{r, density com figs 9}
ginmin = 40000
ginmax = 45000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Section 10
```{r, density com figs 10}
ginmin = 45000
ginmax = 50000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

@@

## {-}

There are a few points of interest to note in these spatial correlation results. First, the no heritability distribution always remains the same (regardless of GA combination or time). When the GA combination has higher mutational variance there is less of a range in the possible spatial correlations, especially when there is no interaction. The spatial correlations in these simulations do not consistently reach the high levels of spatial correlation seen in the real newt and snake population. Experiment D seems to either be more variable in spatial correlation (more spread out, different in different simulation trial) or centered to the just to the left of zero (cor is negative). I think that there is a lot of noise and over lap. From these spatial correlation values I cannot immediately see the difference in all of the GA combinations (there is not one rule I would use to define all of these results).

## Whole Correlation by GA Combinations {.tabset}

This section will focus on the showing the spatial correlation for the whole simulation separated by GA combination. The goal is to see if the overall spatial correlation simulation results differ between experiments. Dashed line is the real newt and snake phenotype correlation value. Colors: red = tall map 5 sections, green = tall map 7 sections, blue = no heritability, purple = no interaction

### Hist
```{r, one big one}

ginmin = 0
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Density
```{r, one big one density}
ginmin = 0
ginmax = 50000
suppressMessages(print(dens_cors_by_gen_col_all_exp_rep(all_cor_exp, "Simulation Correlation Comparied to Real Correlation", "inter", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))

 Again, no heritability stands out as unchanging. At GA combinations where there is low variation red (tall map 5 sections), green (tall map 7 sections), and purple (no interaction) look ver similar. At the genetic variation in one of the species increases, the spatial correlation in no interaction simulation becomes more negative.

## {-}

##  The Highs and the Lows {.tabset}

This section examines the amount of data points that reach and exceed an arbitrary limit. For example, I pick a limit of 0.3, and I would like to count the amount of spatial correlation points are above 0.3 or below -0.3. I can also look at just the positive or negative correlations. The goal of this section is to see how the different experiments (A, B, C, D) vary in the edges of the spatial correlation.

### Positive 0.3

```{r, thresholds 1}

@@

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
```

### Negative 0.3

```{r, thresholds 1a}

file = all_cor_exp
treshold = 0.3
p_n_b = "n"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
```

### Both 0.3 
```{r, thresholds 2}

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
```

### Positive 0.5

```{r, thresholds 2b}

file = all_cor_exp
treshold = 0.5
p_n_b = "p"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
```

### Negative 0.5

```{r, thresholds 2a}

file = all_cor_exp
treshold = 0.5
p_n_b = "n"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
```

### Both 0.5 
```{r, thresholds 3}
file = all_cor_exp
treshold = 0.5
p_n_b = "b"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
```

### Positive 0.7

```{r, thresholds 3b}

file = all_cor_exp
treshold = 0.7
p_n_b = "p"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
```

### Negative 0.7

```{r, thresholds 3a}

file = all_cor_exp
treshold = 0.7
p_n_b = "n"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)
```

### Both 0.7 
```{r, thresholds 4}
file = all_cor_exp
treshold = 0.7
p_n_b = "b"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

@@

@@

### Positive 0.9

```{r, thresholds 5b}
